### 2014-04-16 brains-protocol.tex
Start working on model example figure

The main question in this problem concerns the way we consider later occurrences of a quotation which, when it first appeared, was identified to be an alteration from an original quotation.
\rk{it's a balance between repetition, substitution, or injection from outside/other process from inside}
Let us give an example: say the quotation ``These accusations are false and absurd'' ($q_a$) appears in a blog on January 18, and the slightly different quotation ``These accusations are false and incoherent'' ($q_b$) appears in another blog on the 19th, the 20th, and the 21st of January.
If $q_a$ was sufficiently prominent when $q_b$ first appeared, we can safely assume that the author of $q_b$ on the 19th based himself on $q_a$.
But what about the following occurrences of $q_b$?
Should we consider them to be substitutions based on $q_a$ (i.e. re-creations of $q_b$ by a new instance of the substitution process that brought from $q_a$ to $q_b$ in the first place) or reproductions of the first occurrence of $q_b$?

@@

\begin{figure}[h]
    \centering
    \def\svgwidth{\linewidth}
    \small
    \input{images/substitution-detection-example.pdf_tex}
    \caption{Example substitution detection model}
    \label{fig:substitution-detection-example}
\end{figure}

@@

These various flavours of an ideal substitution detection model essentially change whether occurrences are considered as substitutions from another quote or repetitions of the original quote.

@@

For a given feature $\phi$, the protocol lets us compute substitution \emph{susceptibilities} for each feature value $f$.
We say that a word is \emph{substitutable} if it appears in a quote which undergoes a substitution, whether that substitution operates on the considered word or on another.
Word substitution susceptibility is computed as the ratio of the number $s_w$ of times a word is substituted to the number $p_w$ of times that word appears in a substitutable position, i.e. $\sfrac{s_w}{p_w}$.

>>>>

The main question in this problem concerns the way we consider later occurrences of a quotation that has already occurred earlier: the author of the later occurrences could have sourced an earlier occurrence and accurately copied it, they could have transformed an earlier occurrence of \emph{another} quote into this one, or they could have relied on information or other quotes from outside the dataset, i.e. from an external source we do not measure.

Let us give an example: say the quotation ``These accusations are false and \textbf{absurd}'' ($q_a$) appears in a blog on January 18, and the slightly different quotation ``These accusations are false and \textbf{incoherent}'' ($q_b$) appears in other blogs twice on the 19th and once on the 20th of January.
If $q_a$ was sufficiently prominent when $q_b$ first appeared, we can safely assume that the first author of $q_b$ on the 19th based himself on $q_a$.
But what about the second occurrence of $q_b$ on the 19th, and the one on the 20th?
Should we consider them to be substitutions based on $q_a$ (i.e. re-creations of $q_b$ by a new instance of the substitution process that brought from $q_a$ to $q_b$ in the first place) or reproductions of the first occurrence of $q_b$?

\begin{figure}[h]
    \centering
    \def\svgwidth{\linewidth}
    \small
    \input{images/substitution-detection-example1.pdf_tex}
    \caption{XXXXX}
    \label{fig:substitution-detection-example1}
\end{figure}

@@

@@

These various flavours of an ideal substitution detection model essentially change whether occurrences are considered as substitutions from another quote, repetitions of the original quote, or introduction of information external to the dataset.

@@

For a given feature $\phi$, the protocol lets us compute substitution \emph{susceptibilities} for each feature value $f$.
We say that a word is \emph{substitutable} if it appears in a quote which undergoes a substitution, whether that substitution operates on the considered word or on another.
\rk{We also restrict to words substituted at least once.}
Word substitution susceptibility is computed as the ratio of the number $s_w$ of times a word is substituted to the number $p_w$ of times that word appears in a substitutable position, i.e. $\sfrac{s_w}{p_w}$.
